### 2015-07-05 paper.tex
test git
test merge
paper_1 commit
paper_2
add disk estimation part

>>>>

		\section{The disk storage space estimation}
		Now for the JUNO DAQ(Data Acquisition), we have several promising schemes. 
		If the electronic system can do zero suppression, we can just
		save the fired PMT's output information.
		For the normal
		events we assume the average fired PMT number is 1000, the sampling time window 
		is 1 $\mu$s. Each sampling point will occupy 2 bytes disk storage space, so each
		normal event need about 2MByes disk storage space. For the muon events, all the 
		PMTs will be fired. We assume the total PMT number of the central detector is about 
		17746, so each muon event need about 36MBytes.

		If we can do the waveform compression, we can shorten the sampling time window from
		1 $\mu$s to 50ns. So each normal event need about 0.1MBytes disk storage space, 
		each muon event need about 1.8MBytes.

		If the electronic system can't do zero suppression, we need save all the PMT's output.
		If the sampling time window is 1 $\mu$s, each event will need 36MBytes disk storage space. 
		If we can do 
		waveform compression to shorten the sampling time window from 1 $\mu$s to 50ns, each event
		will need about 1.8MBytes.
